### 2014-08-03 Applications/ImageSegment/ImageSegment.tex
Small edits, to explain some concepts better

Every undirected edge can be represented as two directed edges.
Figure \ref{fig:example_graph} shows a simple undirected graph.
The graph in Figure \ref{fig:example_graph} can be represented as the following adjacency matrix.
\[
A = \begin{pmatrix}
0 & 1 & 0 & 0 & 1 & 0\\
1 & 0 & 1 & 0 & 1 & 0\\
0 & 1 & 0 & 1 & 0 & 0\\
0 & 0 & 1 & 0 & 1 & 1\\
1 & 1 & 0 & 1 & 0 & 0\\
0 & 0 & 0 & 1 & 0 & 0
\end{pmatrix}
\]
For undirected graphs, the adjacency matrix will always be symmetric.
The diagonal represents self-edges, or edges that connect a node to itself.

Raising the adjacency matrix to a power yields some very interesting information.
We can discover the number of paths of length $n$ between two nodes by raising a graph's adjacency matrix to the $n$th power.
For example, by squaring $A$, we can find the number of paths of length 2 between every pair of nodes.
\begin{lstlisting}
>>> A = np.array([[0,1,0,0,1,0],[1,0,1,0,1,0],
                  [0,1,0,1,0,0],[0,0,1,0,1,1],
                  [1,1,0,1,0,0],[0,0,0,1,0,0]])
>>> np.linalg.matrix_power(A,2)
array([[2, 1, 1, 1, 1, 0],
       [1, 3, 0, 2, 1, 0],
       [1, 0, 2, 0, 2, 1],
       [1, 2, 0, 3, 0, 0],
       [1, 1, 2, 0, 3, 1],
       [0, 0, 1, 0, 1, 1]])
\end{lstlisting}
We can see that no paths of length 2 exist between node 0 and node 5 because $A^2_{0,5} = 0$.
By calculating $A^6$ we can find the number of paths length 6 from node 3 to itself.
\begin{lstlisting}
>>> np.linalg.matrix_power(A, 6)
array([[45, 54, 38, 45, 54, 16],
       [54, 86, 29, 77, 51, 11],
       [38, 29, 55, 15, 70, 27],
       [45, 77, 15, 75, 31,  4],
       [54, 51, 70, 31, 93, 34],
       [16, 11, 27,  4, 34, 14]])
\end{lstlisting}
We see that there are 55 unique paths of length 6 from node 3 to itself.
Imagine trying to count all of those paths by hand!
It would be very easy to count incorrectly.
However, this method makes it very simple to count paths without any mistakes.

@@

Another useful way of representing an undirected graph is a Laplacian matrix.
This special matrix can reveal a lot of information about a graph.
\begin{definition}
For a simple graph (an unweighted, undirected graph without self-edges), the Laplacian of a graph $G$ is
\[ L_G = D_G - A_G \]
where $D_G$ is the degree matrix of $G$ and $A_G$ is the adjacency matrix of $G$.
\end{definition}
An important question in working with graphs is the degree of its nodes.
The degree of a node is the number of edges that connect to the node.
For a directed graph, each node has an \emph{out-degree} (the number of edges directed away from a node) and an \emph{in-degree} (the number edges directed toward a node).
The degree matrix of a graph is a diagonal matrix that has the degree of each node as the diagonal entries (thus, for a directed graph there in an in-degree matrix and an out-degree matrix).

>>>>

Every undirected edge can be represented as two directed edges.
Figure \ref{fig:example_graph} shows a simple undirected graph.
The graph in Figure \ref{fig:example_graph} can be represented by the following adjacency matrix.
\[
A = \begin{pmatrix}
0 & 1 & 0 & 0 & 1 & 0\\
1 & 0 & 1 & 0 & 1 & 0\\
0 & 1 & 0 & 1 & 0 & 0\\
0 & 0 & 1 & 0 & 1 & 1\\
1 & 1 & 0 & 1 & 0 & 0\\
0 & 0 & 0 & 1 & 0 & 0
\end{pmatrix}
\]
For undirected graphs, the adjacency matrix will always be symmetric.
The diagonal represents self-edges, or edges that connect a node to itself.

Raising the adjacency matrix to a power yields some very interesting information.
We can discover the number of paths of length $n$ between two nodes by raising a graph's adjacency matrix to the $n$th power.
For example, by squaring $A$, we can find the number of paths of length two between every pair of nodes.
\begin{lstlisting}
>>> A = np.array([[0,1,0,0,1,0],[1,0,1,0,1,0],
                  [0,1,0,1,0,0],[0,0,1,0,1,1],
                  [1,1,0,1,0,0],[0,0,0,1,0,0]])

>>> np.linalg.matrix_power(A,2)
array([[2, 1, 1, 1, 1, 0],
       [1, 3, 0, 2, 1, 0],
       [1, 0, 2, 0, 2, 1],
       [1, 2, 0, 3, 0, 0],
       [1, 1, 2, 0, 3, 1],
       [0, 0, 1, 0, 1, 1]])
\end{lstlisting}
We can see that no paths of length two exist between node 0 and node 5 because $A^2_{0,5} = 0$.
By calculating $A^6$ we can find the number of paths of length six from node 3 to itself.
\begin{lstlisting}
>>> np.linalg.matrix_power(A, 6)
array([[45, 54, 38, 45, 54, 16],
       [54, 86, 29, 77, 51, 11],
       [38, 29, 55, 15, 70, 27],
       [45, 77, 15, 75, 31,  4],
       [54, 51, 70, 31, 93, 34],
       [16, 11, 27,  4, 34, 14]])
\end{lstlisting}
We see that there are 75 unique paths of length six from node 3 to itself.
Imagine trying to count all of those paths by hand!
It would be very easy to count incorrectly.
This method makes it very simple to count paths without mistakes.

@@

An important question in working with graphs is the degree of its nodes.
The degree of a node is the number of edges that connect to the node.
For a directed graph, each node has an \emph{out-degree} (the number of edges directed away from a node) and an \emph{in-degree} (the number edges directed toward a node).
The degree matrix of a graph is a diagonal matrix that has the degree of each node as the diagonal entries (thus, for a directed graph there is an in-degree matrix and an out-degree matrix).

Another useful way of representing an undirected graph is a Laplacian matrix.
This special matrix can reveal a lot of information about a graph.
\begin{definition}
For a simple graph (an undirected graph without self-edges), the Laplacian of a graph $G$ is
\[ L_G = D_G - A_G \]
where $D_G$ is the degree matrix of $G$ and $A_G$ is the adjacency matrix of $G$.
\end{definition}
